\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classification of the Yelp's Restaurants}

### 2016-01-16 paper/article_2.tex
update report

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Userless Classification for the Yelp Dataset Challenge} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

@@

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classification for the Yelp Dataset Challenge}} % Article title

\author{
\large
\textsc{Nicolas Drizard \& Virgile Audi}\\[2mm] % Your name
\normalsize Final Project for CS281, Harvard University \\ % Your institution
\normalsize {nicolas.drizard@g.harvard.edu \quad vaudi@g.harvard.edu} % Your email address
\vspace{-5mm}
}
\date{}

@@

Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques. To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using online variational inference (OVI), and benchmark it with the LDA using a Gibbs samplingmethod (GS) and the Non Negative Matrix Factorisation (NMF). We then present two methods for classifying restaurants. We first resorted to a supervised approach with one-vs-all classifiers on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in counts. The second approach is unsupervised, using the Walktrap Algorithm, a community detection algorithm on network of restaurant. If the different feature extraction methods performs differently for the supervised and unsupervised approach, we observe some very promising results. The results could be used as the first step to an automated categorization system on the Yelp website.

@@

\lettrine[nindent=0em,lines=1]{T}he classification system in Yelp is manual. When the owner of a business creates a page for his restaurant or bar, he is can provide a certain number of labels. Yelp users can then alter or even add new tags based on their experiences. As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of entries classification. Our ultimate objective is to create an automatised method to classify the businesses, based on their properties and most importantly on their reviews from Yelpers. \\

This project can be divided in three parts. First, to extract feature, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to embed the reviews into a geometrical space. Then, we applied supervised learning methods to evaluate how relevant are the feature to predict the labels. Last, we built an unsupervised clustering method using the Walktrap algorithm.

@@

\noindent For simplicity, we chose to focus on restaurants and bars in the city of Las Vegas, Nevada. This reduced the data to a dataset of 3822 businesses, with about 20 thousands reviews and 250 other features per entry such as hours, parking availabity, take-out, ambience. If the numerical data provided by Yelp is mostly cleaned, it was not the case of the text data. Cleaning the reviews represented a significant part of this final project. We present some of the steps we followed in the process:\\

\begin{compactitem}
    \item We aggregated all the reviews about a particular business into a "super" review, in order to get a general sense of what the restaurant was about;
    \item We applied spelling corrections, removed common stopwords and generic words such as "table" or "restaurants";
    \item We attempted at only selecting common words and not adjectives in order to focus on what the venues were about and not the users' opinions (this process was done taking advantage of Spark to reduce the computing time);
    \item We transformed the corpus of "super reviews" into a document-term matrix that we could exploit;
    \item As we aggregated the reviews, some words may be more prevalent than others, so we scaled the words counts into the range [0, 100] for each review.
\end{compactitem}

@@

To extract content from the reviews, we applied two methods from topic modeling to reduce the document term matrix into meaningful information. We first looked at LDA, using both a Gibbs sampler (GS) and an Online Variational Inference (OVI) algorithm. Note that we used the Gibbs sampler as a way to benchmark our own version of OVI. The motivation behind OVI is twofold. First, it appeared more appropriate to the data we were working with, indeed new reviews can always be added to the corpus in continuous flow. Second, it showed some extremely significant time improvement over the Gibbs sampler version in Python. We also wanted to compare the performance of LDA with a non-probabilistic approach which is the NMF.

@@

\noindent This distribution is intractable. As mentioned above, we used two  methods to infer it: through a Gibbs sampler or variational inference. In the first case, we are estimating the hyper parameters $\theta$ and $\phi$ with samples on the different variables. Alternatively, we chose the online variational inference method which finds the variational parameters that optimize a lower bound on the loglikelihood. The setup \cite{OLLD} of the variational inference is as follows. We first approximate the true posterior by a simpler and factorised distribution:

@@

\noindent The $\boldsymbol{\gamma}$ parameter rule the topic assignments for each document and the $\boldsymbol{\lambda}$, the topics themselves. We then minimise the KL divergence between the distribution $q$ and the true posterior $p$. What differs in the online variational inference is that we sample a mini-batch of document at each step and perform the E-step as if this mini-batch constituted the entire corpus. We present the algorithm below:

@@

\noindent where $\kappa \in (0.5,1]$ rules how fast we forget old values of $\tilde{\lambda}$ and $\tau_{0}$ how much weight one wants to put on the first iterations. $\alpha$ and $\eta$ where fixed at the same value $\frac{1}{|D|}$.

@@

We need a measure to evaluate the performance of our model and to tune the hyperparameters. We use the perplexity on held-out data as a measure of our model fit. The perplexity is defined as the geometric mean of the log likelihood of the words in the held-out set of documents given the trained model. In our case, for each document we held out 20\% of the words which constitue the validation set to apply a 5-fold cross-validation.

@@

\noindent We used this measure to optimize the number of topics K and the hyper parameters $\kappa$, $\tau$ of the optimization. We also used the perplexity on the training set to benchmark our algorithm with the Gibbs sampler in the LDA 1.0.3 package in Python:

@@

\noindent We obtained similar results using the NMF approach. The topics themselves were not our primary interested. As mentioned in the introduction, we were using these methods primarly for dimensional reduction purposes. \\

We would like to make a general comment about the online variational algorithm. We noticed that its algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weith parameter $\tau$. This was also noted by Tamara Broderick, Nicholas Boyd, Andre Wibisono and Ashia C. Wilson in their paper\cite{svi}. In addition to validating the number of topics, validating over these parameters was crucial to obtain valuable results.\\

@@

\noindent The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the LDA and on the other hand, the properties provided by Yelp. Pre-processing the latter part provided a 198 dimensional vector. These features contained both numerical values (rating, space coordinates, number of reviews, customer check-in...) and categorical ones which we converted into indicator variables.\\

\noindent Given our numerical features, many different discriminative and generative models could be appllied on our data. Nonetheless, the indicator features are sparse and the data are really noisy. We therefore needed to consider a penalized or aggregated model to reduce overfitting.\\

\noindent We chose a one-vs-all approach to tackle this multi-label task, and built one binary classifier for each label. We then assign to the entries the labels predicted by each model. The goal is here to explore how the different models perform and to tune them to come up with the best estimator. We developped our own L2 penalized logistic regression and used \emph{scikit-learn} \cite{sklearn} for the other models.

@@

@@

\noindent We decided to reduce the dimension of the dataset before fitting our model. As the high-dimensionality is largely due to the customer check-in counts and as they share a common structure, we decided to project them in an euclidean space. The combination of the embedded features with the latent features provided by the reviews is more consistent. We apply a principal component analysis (PCA) while keeping \textbf{95\%} of the variance which reduces the dimension from \textbf{168} to \textbf{19}.

@@

\noindent Here we provide the different results we obtained from our models. We ran one-vs-one classifiers for the 10 different labels which are the most represented in the Las Vegas restaurants. Then we evaluated for each classifier its accuracy and averaged them to get the evaluation metric printed in the table. We tested them on three different kinds of features provided by the reviews depending on the method used to build them. Then we ran each model on the PCA projection and on the raw data. We also show for comparaison the baseline model where we do not assign any label. This result is really high because of the skewness of the considered sample, among the 10 categories considered for 3822 restaurants the most represented (Fast Food) contains 553 entries and the least (American New) 280 entries.

@@

\noindent The first outcome of this comparative study is the differences between each feature extraction method. The model built with the GS features seems to outperform on average the other two, which perform similarly to each other. These results are not surprising as the variationnal inference learns the closest model to the underlying one in terms of KL divergence. With the Gibbs sampling approach, we approximate the true underlying distribution at each iteration to refine our estimator. As a result, the latter method is by nature better to find the best model as long as it has enough iteration to converge and there actually exists an underlying mixture models. Nevertheless, the OVI remains a good proxy with regard to its time execution (53s against 50min for the Gibbs Sampler).\\

\noindent If we then compare the models to each other, we see that the support vector machine performs poorly and that the linear version was even closer to the baseline. This confirms that the data is not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate. The logistic regression performs better under the l1 penalization because of the sparsity of our features. Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\

\noindent We plotted here the ROC curves of the Random forest for the 10 classes considered. The ranking with respect to the area under the curve is very close to the one induced by the number of positive elements for each class.This shows that the more positive elements we have, the better the model actually performs. Nonetheless, trying to learn the model on a smaller and more balanced train set for the classes with a low number of positive elements does not improve the classification accuracy.

@@

@@

\noindent Once we found a sufficiantly good estimator, we investigated the weights it assigned to each feature. This provided an answer to two important questions: \textit{Are the feature extracted from the reviews more relevant than the one provided by Yelp to classify the restaurants by category? Among the features extracted by the review, can we identify for each category one or several highly discriminative features?} Moreover, we can compare the performance of the two different LDA we used.\\

\noindent We answer these questions with a comparative study on four specific categories (Fast Food, Pizza, Nightlife and Bars) with a Random Forest on four kinds of features, depending on the type of LDA used and the reduction with PCA. The results with the features built with an NMF are similar to those with the OVI. We used the measure provided by scikit learn to evaluate the importance of the features. It is defined as the total decrease in node impurity averaged over all trees of the ensemble.

@@

\noindent First, considering the results for the OVI features, we observe that some properties provided by Yelp are discriminative for our classification. For example, the attribute \textit{Good for Kids} helps to sort the Bars and the Nightlife categories which is not surprising. The Fast Food may be the restaurants with the largest number of reviews as they have the largest number of customers, the model confirms this with the high weight on the \textit{reviews\_count}. This is also a cheap restaurant, hence the importance of the price range. As a result, it is worth considering the features provided by Yelp as they help discriminate the entries.\\

\noindent Second, for the Pizza category with the features extracted by the OVI we observe a discriminative feature which matchs the one about Pizza provided in the figure 3. Then, for the same LDA method, there is no discriminative feature for the other categories. Now, if we consider the results for the GS features, each category has a highly discriminative feature. Moreover, if we look at the most common words for each of these topics in the figure 10, we naturally understand their importance in the classification. This result confirms our analysis on the models. The Gibbs sampling method provides a finer topic distribution over the documents (here it is a label distribution over the restaurants).

\noindent Lastly, it is worth noticing the effect of the PCA on the feature importance. For both the OVI and the GS, if we look back at the Pizza category, the results with the PCA are much more clear-cut. The weight of the most important feature and its difference with those of the other features are higher. We can explain this by the fact that the projection gave more structure to the data and reduces the noise.\\

\noindent This part was about confronting our data to supervised methods to grasp their patterns and also coming up with a good classification. We provided empirical results to confirm the difference between the two common LDA methods and proved that with the Gibbs sampling, the LDA can be really efficient at finding the underlying topics on a set of documents.  It also proved that it performed much butter than a matrix factorization method. Related to our problem, it showed us that if numerical features provided by Yelp contained some information, the LDA features remained much more important when looking to find the labels of a restaurant.

@@

For this part of the project, we use the same features as for the supervised classification approach, i.e. the topic assignments. We wanted to see if it was possible to retrieve the original classification only based on the reviews. To do so and in order to check if our classification attempt was successful, we sampled about 1000 restaurants having tags in the following list of 6 categories: Sushi, Steakhouse, Seafood, Mexican, Sports and Breakfast \& Brunch. We then applied applied the following methodology.\\

@@

\noindent The choice of having a non-zero weight between two restaurants even though they are not "close" is motivated by the fact that many graph clustering algorithm, in particular the WalkTrap algorithms that we used, only work on a connected graph.\\

@@

We ran the algorithm from the \emph{igraph} \cite{igr} package in R on the three graphs generated with the three approaches mentionned above (NMF, OVI LDA, GS LDA). The results where extremely similar. We outputted a dendogram (cf. Annex) representing the obtained clustering. We colored the tag of each business for a better readability.  It is not yet entirely clear to us how to get the optimum number of clusters. We were puzzled to see that the Walktrap algorithm indicated that a cut into three big clusters represented the optimum partition. Knowing the structure of the sampled restaurants, we decided to further investigate the dendogram. As one can see on Figure 3, cutting the tree at different heights, we can obtain five clear colored communities, corresponding to five of the six tags we pre-selected.\\

@@

\noindent It seems that this method will succeed in making a difference between communities of restaurants if they are almost exlusive. It seems very unlikely to discover a restaurant that one can identify as both a Mexican and a Sushi place or even a Sushi place specialising in Breakfast (unless its speciality is the takagoyaki, a type of Japanese omelette made by "rolling together several layers of cooked egg"). It was often the case that misclassified restaurants had the tag "Buffet" which is for our purpose of classification our worst ennemy as it will phagocytose many categories at once.

@@

So far, we managed to extract the categories of the restaurants as latent features with a latent dirichlet allocation algorithm on the aggregated reviews for each restaurant. \\

Futur work could focus on the sub-cliques and try to get a finer classification by combining them with other features like check-ins, parking availability, etc. As a variant, we could also try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.\\

As a variant, we could try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses. Lastly, this method is applicable on each review separately to predict the rating of the review, with a supervised lda also to avoid the predominance of the categories in the topics.

@@

This study illustrates different methods to extract feature from a set of documents. The results confirmed that the latent Dirichlet allocation manages to grasp the underlying features. The comparison with the supervised learning methods confirmed the importance of the feature extraction part in a machine learning problem. It also corroborates the assumption that the features of the businesses could be used to infer their category labels. Finally, the unsupervised clustering process we developped provides encouraging results and could result in an automation tool for Yelp to label properly its database.

>>>>

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Userless Classification of the Yelp's Restaurants} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

@@

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classification of the Yelp's Restaurants}} % Article title

\author{
\large
\textsc{Nicolas Drizard \& Virgile Audi}\\[2mm] % Your name
\normalsize Final Project for CS281, Harvard University \\ % Your institution
\normalsize {nicolasdrizard@g.harvard.edu \quad vaudi@g.harvard.edu} % Your email address
\vspace{-5mm}
}
\date{}

@@

Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques. To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using online variational inference (OVI), and benchmark it with the LDA using a Gibbs sampling method (GS) and the Non Negative Matrix Factorization (NMF). We then present two methods for classifying restaurants. We first resorted to a supervised approach with one-vs-all classifiers on the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in counts. The second approach is unsupervised, using a community detection algorithm on the network of restaurants, the Walktrap algorithm. If the features extraction methods perform differently for the supervised and unsupervised approaches, we observe some very promising results. Theses insights could be used as the first step to an automated categorization system on the Yelp website.

@@

\lettrine[nindent=0em,lines=1]{T}he classification system in Yelp is manual. When the owner of a business creates a page for his restaurant or bar, he can provide a certain number of labels. Yelp users can then alter or even add new tags based on their experiences. As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of entries classification. Our ultimate objective is to create an automatised method to label the businesses, based on their properties and most importantly on their reviews from Yelpers. The new tags could be added to the existing tags to build a finer classification. \\

This project can be divided in three parts. First, to extract the features, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorization (NMF) to embed the reviews into a geometrical space. Then, we applied supervised learning methods to evaluate how much information the features carry. Last, we built an unsupervised clustering method using a community detection algorithm.

@@

\noindent For simplicity, we chose to focus on restaurants and bars in the city of Las Vegas, Nevada. This reduced the data to a dataset of 3 822 businesses, with about 20 thousands reviews and 250 other features per entry such as hours, parking availabity, take-out, ambience. If the numerical data provided by Yelp is mostly cleaned, it was not the case for the text data. Cleaning the reviews represented a significant part of this project. Here are some of the steps we followed in the process:\\

\begin{compactitem}
    \item We aggregated all the reviews about a particular business into a "super" review, in order to get a general sense of what the restaurant was about (this was possible because we don't need to differentiate the users writing the reviews);
    \item We applied spelling corrections, removed common stopwords and generic words such as "table" or "restaurants";
    \item We attempted at only selecting common words, removing the adjectives, in order to focus on what the venues were about and not the users' opinions (this process was done taking advantage of Spark to reduce the computing time);
    \item We transformed the corpus of the "super reviews" into a document-term matrix that we could exploit;
    \item As we aggregated the reviews, some words may be more prevalent than others, so we scaled the words counts into the range [0, 100] for each review. (this step produced a finer words distribution for each topic of the LDA)
\end{compactitem}

@@

To extract content from the reviews, we applied two methods from topic modeling to reduce the document term matrix into meaningful information. We first looked at LDA, using both a Gibbs sampler (GS) and an Online Variational Inference (OVI) algorithm. Note that we used the Gibbs sampler as a way to benchmark our own version of OVI. The motivation behind OVI is twofold. First, it appeared more appropriate to the data we were working with. If some restaurants have already enough reviews to be classified accurately, most of them could have finer labels with more reviews. Moreover, some nuances may appear over the time among the clusters of restaurants. As a result, we should be able to add the new reviews to the corpus in a continuous flow. Second, it showed some extremely significant time improvements over the Gibbs sampler version in Python. Nonetheless, a major drawback of this method is the high sensitivity to the hyperparameters. We also wanted to compare the performance of LDA with a non-probabilistic approach which is the NMF.

@@

\noindent This distribution is intractable. As mentioned above, we used two  methods to infer it: with a Gibbs sampler and with variational inference. In the first case, we are estimating the hyperparameters $\theta$ and $\phi$ with samples on the different variables. Alternatively, we chose the online variational inference method which finds the variational parameters that optimize a lower bound on the loglikelihood. The setup \cite{OLLD} of the variational inference is as follows.

\noindent We first approximate the true posterior by a simpler and factorised distribution:

@@

\noindent The $\boldsymbol{\gamma}$ parameter rules the topic assignments for each document and the $\boldsymbol{\lambda}$ the topics themselves. We then minimise the KL divergence between the distribution $q$ and the true posterior $p$. What differs in the online variational inference is that we sample a mini-batch of document at each step and perform the E-step as if this mini-batch constituted the entire corpus. We present the algorithm below:

@@

\noindent where $\kappa \in (0.5,1]$ rules how fast we forget the old values of $\tilde{\lambda}$ and $\tau_{0}$ how much weight one wants to put on the first iterations. $\alpha$ and $\eta$ were fixed at the same value $\frac{1}{|D|}$.

@@

We need a measure to evaluate the performance of our model and to tune the hyperparameters. We use the perplexity on held-out data as a measure of our model fit. The perplexity is defined as the geometric mean of the log likelihood of the words in the held-out set of documents given the trained model. In our case, for each document we held out 20\% of the words which constitute the validation set to apply a 5-fold cross-validation.

@@

\noindent We used this measure to optimize the number of topics K and the hyperparameters $\kappa$, $\tau$ of the optimization. We also used the perplexity on the training set to benchmark our algorithm with the Gibbs sampler in the LDA 1.0.3 package in Python:

@@

\noindent We obtained similar results using the NMF approach. As mentioned in the introduction, the topics themselves were not our primary interested, we were using these methods for dimensional reduction purposes. \\

We would like to make a general comment about the online variational algorithm. We noticed that its algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weight parameter $\tau$. This was also noted by Tamara Broderick, Nicholas Boyd, Andre Wibisono and Ashia C. Wilson in their paper\cite{svi}. Validating the number of topics and these parameters was indeed crucial to obtain valuable results.\\

@@

\noindent The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the topic modeling algorithm (LDA or NMF) and on the other hand, the properties provided by Yelp. Pre-processing the latter part provided a 198 dimensional vector. These features contained both numerical values (rating, space coordinates, number of reviews, customer check-in...) and categorical ones which we converted into indicator variables.\\

\noindent Given our numerical features, many discriminative and generative models could be applied on our data. Nonetheless, the indicator features are sparse and the data are really noisy. We therefore needed to consider a penalized and/or aggregated model to reduce the overfitting.\\

\noindent We chose a one-vs-all approach to tackle this multi-label task and built one binary classifier for each label. We then assigned to the entries the labels predicted by each model. The goal is here to explore how the different models perform and to tune them to come up with the best estimator. We developped our own L2 penalized logistic regression and used \emph{scikit-learn} \cite{sklearn} for the other models.

@@

In our experiments, we focused on the 10 most represented labels in the Las Vegas restaurants, which constitute our set of outputs. A same restaurant may have more than one label as we consider a multi-label classification.

@@

\noindent We decided to reduce the dimension of the second part of the dataset (the properties provided by Yelp) before fitting our model. As the high-dimensionality is largely due to the customer check-in counts and as they share a common structure, we decided to project them in an euclidean space. Combining these embedded features with those provided by the reviews produced then a more consistent dataset. This dimensionality reduction was done with a principal component analysis (PCA), keeping \textbf{95\%} of the variance which reduces the dimension from \textbf{168} to \textbf{19}.

@@

\noindent Here we provide the different results we obtained with our models. We ran one-vs-one classifiers for the 10 labels. Then we evaluated for each classifier its accuracy and averaged them to get the evaluation metric printed in the table. We also plotted the ROC curves for a specific model.

\noindent We tested them on three different kinds of features provided by the reviews depending on the method used to build them (\textit{see the columns}). Then, for each model, we used both the raw features provided by Yelp and those embedded by the PCA projection (\textit{see the rows}). We also show for comparison the baseline model where we do not assign any label. This result is really high because of the skewness of the considered sample: among the 10 categories considered for 3 822 restaurants, the most represented (Fast Food) contains 553 entries and the least (American New) 280 entries.

@@

\noindent The first outcome of this comparative study is the differences between each feature extraction method. The model built with the GS features seems to outperform on average the other two, which perform similarly to each other. These results are not surprising as the variationnal inference learns the closest model to the underlying one in terms of KL divergence. With the Gibbs sampling approach, we approximate the true underlying distribution at each iteration to refine our estimator. As a result, the latter method is by nature better to find the best model as long as it has enough iterations to converge and there actually exists an underlying mixture models. Nevertheless, the OVI remains a good proxy with regard to its time execution (53s against 50min for the Gibbs Sampler).\\

\noindent If we then compare the models to each other, we see that the support vector machine performs poorly and that the linear version was even closer to the baseline. This confirms that the data are not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate. The logistic regression performs better under the l1 penalization because of the sparsity of our features. Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\

@@

\noindent We plotted here the ROC curves of the Random forest for the 10 classes considered. The ranking with respect to the area under the curve is very close to the one induced by the number of positive elements for each class. This shows that the more positive elements we have, the better the model actually performs. Nonetheless, learning the model on a smaller and more balanced train set with regards to the predicted class, i.e. with a lower number of negative elements, did not improve the classification accuracy.

@@

\noindent Once we found a sufficiantly good estimator, we investigated the weights it assigned to each feature. This provided an answer to two important questions: \textit{Are the feature extracted from the reviews more relevant than the one provided by Yelp to classify the restaurants by category? Among the features extracted by the reviews, can we identify for each category one or several highly discriminative features?} Moreover, we can compare the performance of the two different LDA we used.\\

\noindent We answer these questions with a comparative study on four specific categories (Fast Food, Pizza, Nightlife and Bars) with a Random Forest on four kinds of features, depending on the type of LDA used and the reduction with PCA. The results with the features built with an NMF are similar to those with the OVI. We used the measure provided by scikit learn to evaluate the importance of the features. It is defined as the total decrease in node impurity averaged over all the trees of the ensemble.

@@

\noindent First, considering the results for the OVI features, we observe that some properties provided by Yelp are discriminative for our classification. For example, the attribute \textit{Good for Kids} helps to sort the Bars and the Nightlife categories. The Fast Food may be the restaurants with the largest number of reviews as they have the largest number of customers, the model confirms this with the high weight on the \textit{reviews\_count}. This is also a cheap restaurant, hence the importance of the price range. As a result, it is worth considering the features provided by Yelp as they help discriminate the entries.\\

\noindent Second, for the Pizza category with the features extracted by the OVI we observe a discriminative feature which matchs the one about Pizza provided in the figure 3. Then, for the same LDA method, there is no discriminative feature for the other categories. Now, if we consider the results for the GS features, each category has a highly discriminative feature. Moreover, if we look at the most common words for each of these topics in the figure 6, we naturally understand their importance in the classification. This result confirms our analysis on the models. The Gibbs sampling method provides a finer topic distribution over the documents (here it is a label distribution over the restaurants).

\noindent Lastly, it is worth noticing the effect of the PCA on the feature importance. For both the OVI and the GS, if we look back at the Pizza category, the results with the PCA are much more clear-cut. The weight of the most important feature and its difference with those of the other features are higher. We can explain this by the fact that the projection gave more structure to the data and reduced the noise.\\

\noindent This part was about confronting our data to supervised methods to grasp their patterns and also coming up with a good classification. We provided empirical results to confirm the differences between the two common LDA methods and proved that with the Gibbs sampling, the LDA can be really efficient at finding the underlying topics on a set of documents. It also performed much better than a matrix factorization method. Related to our problem, this showed us that if the numerical features provided by Yelp contained some information, the LDA features remained much more important when looking for the labels of a restaurant.

@@

For this part of the project, we use the same features as for the supervised classification approach, i.e. the topic assignments. We wanted to see if it was possible to retrieve the original classification only based on the reviews. To do so and in order to check if our classification attempt was successful, we sampled about 1000 restaurants having tags in the following list of 6 categories: Sushi, Steakhouse, Seafood, Mexican, Sports and Breakfast \& Brunch. We then applied the following methodology:\\

@@

\noindent The choice of having a non-zero weight between two restaurants even though they are not "close" is motivated by the fact that many graph clustering algorithm, in particular the WalkTrap, only work on a connected graph.\\

@@

We ran the algorithm from the \emph{igraph} \cite{igr} package in R on the three graphs generated with the three approaches mentionned above (NMF, OVI LDA, GS LDA). The results were extremely similar. We outputted a dendogram (cf. figure 12) representing the obtained clustering. We colored the tag of each business for a better readability.  It is not yet entirely clear to us how to get the optimum number of clusters. We were puzzled to see that the Walktrap algorithm indicated that a cut into three big clusters represented the optimum partition. Knowing the structure of the sampled restaurants, we decided to further investigate the dendogram. As one can see on Figure 3, cutting the tree at different heights, we can obtain five clear colored communities, corresponding to five of the six tags we pre-selected.\\

@@

\noindent It seems that this method will succeed in making a difference between communities of restaurants if they are almost exlusive. It seems very unlikely to discover a restaurant that one can identify as both a Mexican and a Sushi place or even a Sushi place specialising in Breakfast (unless its speciality is the takagoyaki, a type of Japanese omelette made by "rolling together several layers of cooked egg"). It was often the case that misclassified restaurants had the tag "Buffet" which is for our purpose of classification our worst ennemy as it will stand for many categories at once.

@@

So far, we managed to extract the categories of the restaurants as latent features with a Latent Dirichlet Allocation algorithm on the aggregated reviews for each restaurant. \\

Future work could focus on the sub-cliques and try to get a finer classification by combining them with other features like check-ins, parking availability, etc. As a variant, we could also try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses. Lastly, as interpretability does not matter, we could try neural architectures to build the features.

@@

This study illustrates different methods to extract features from a set of documents. The results confirmed that the Latent Dirichlet Allocation manages to grasp the underlying features. The comparison with the supervised learning methods confirmed the importance of the features extraction part in a machine learning problem. It also corroborates the assumption that the features of the businesses could be used to infer their category labels. Finally, the unsupervised clustering process we developped provides encouraging results and could result in an automation tool for Yelp to label properly its database.

\section*{Code}

The code for this project can be found at the following address:

\begin{center}
www.github.com/nicodri/CS281
\end{center}
